Measuring sustainability with Australian vine growers using a Bayesian Network

### 2023-10-31 article.tex
Korb an dNicholson notes done!

Korb and Nicholson also describe 8 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
\subsection{The process}
\subsubsection{Parameterizing before evaluating the structure}
\begin{enumerate}
        \item Are the nodes in the BN the right ones?
        \item Are the state spaces (values) for each node correct?
        \item Are the arcs right?
\end{enumerate}
If the answer to any of the above questions is no; then the structure will not be sufficiently defined for the parametarisation of the CPT. In this paper we explicitly defined the structure of the BN prior to CPT parametarisation. This involved:
\begin{enumerate}
        \item exposing the panel to a strawman model in an intial workshop
        \item Describing the model and the process invovled in defining the structure of a BN
        \item The expert panel reviewing possible nodes and arcs, defining their own structures prior to a second workshop (with correspondence between expert panel members prior to the next workshop)
        \item A second workshop to agree upon the final structure of the model
\end{enumerate}
\subsubsection{Trying to build the full model all at once}
Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
\begin{enumerate}
        \item dividing models into subcomponents
        \item breaking down the problem into a single target variable
        \item reducing the scope of the problem
        \item Setting a single time frame for the problem
\end{enumerate}
The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards. This also reduced the BN to a single terminal node. It was further decided to create the BN as a single season to limit its complexity.

\subsection{The problem}
\subsubsection{Not understanding the problem context, complexity without value.}
It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
\begin{enumerate}
        \item what do you want to reason about?
        \item What dont you know?
        \item What infomration do you have?
        \item What do you know?
These questions are well addressed in prior research. The creation of baseline models showed strong linear relationships between many variables. The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability. here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
\end{enumerate}
\subsection{Structure - Nodes}
\subsubsection{Getting the node values wrong. An exhaustive list below}
\begin{enumerate}
        \item Node values aren't exhaustive
        \item Node values aren't exhaustive
        \item Node values aren't mutually exclusive
        \item Incorrect modelling of mutually exclusive outcomes
        \item Trying to model fuzzy categories
        \item Confusing state and Probability
        \item Confusion about what the node represents
\end{enumerate}
Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroberated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
\subsection{Structure Arcs}
\subsubsection{Getting the arc directions wrong}
Arc directions are commonly wrong for the following reasons:
\begin{enumerate}
        \item Modelling reasoning rather than causation
        \item Inverting cause and effect
        \item Missing variables
\end{enumerate}
To note: Korb and Nicholson do not actually suggest a method for overcoming these problems. There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation. It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
\subsubsection{Too many parents}
Sometimes it is unavoidable that a node is affected by many factors, or other nodes. There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child. This technique was employed in the creation of the structure of the BN with the expert panel.
\subsection{Parameters}
\subsubsection{Experts estimates of probabilities are biased}
\begin{enumerate}
        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison. "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.

\end{enumerate}
We have attempted to overcome this with two methods. A diverse and varried expert panel. Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale. With some experts being more specialised in specific areas such as agro-chemicals.
\subsubsection{Incoherent/Incoherent probabilities}
The collection of probabilities for when the CPT is large can result in inconsistent probabilities. The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}. In this study we overcame this through the use of worded response such as high and low. We then assigned probabilities to those broader cases. We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
% \item Inconsistent "filling in" of large CPTs:
-       -       - Being dead certain.

>>>>

Korb and Nicholson also describe 16 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
\subsection{The process}
\subsubsection{Parameterizing before evaluating the structure}
\begin{enumerate}
        \item Are the nodes in the BN the right ones?
        \item Are the state spaces (values) for each node correct?
        \item Are the arcs right?
\end{enumerate}
If the answer to any of the above questions is no; then the structure will not be sufficiently defined for the parametarisation of the CPT. In this paper we explicitly defined the structure of the BN prior to CPT parametarisation. This involved:
\begin{enumerate}
        \item exposing the panel to a strawman model in an intial workshop
        \item Describing the model and the process invovled in defining the structure of a BN
        \item The expert panel reviewing possible nodes and arcs, defining their own structures prior to a second workshop (with correspondence between expert panel members prior to the next workshop)
        \item A second workshop to agree upon the final structure of the model
\end{enumerate}
\subsubsection{Trying to build the full model all at once}
Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
\begin{enumerate}
        \item dividing models into subcomponents
        \item breaking down the problem into a single target variable
        \item reducing the scope of the problem
        \item Setting a single time frame for the problem
\end{enumerate}
The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards. This also reduced the BN to a single terminal node. It was further decided to create the BN as a single season to limit its complexity.

\subsection{The problem}
\subsubsection{Not understanding the problem context, complexity without value.}
It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
\begin{enumerate}
        \item what do you want to reason about?
        \item What dont you know?
        \item What information do you have?
        \item What do you know?
These questions are well addressed in prior research. The creation of baseline models showed strong linear relationships between many variables. The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability. here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
\subsubsection{Complexity without value}
A very common impulse, when something isk nown about thep roblem, is to want to put it in the model. But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value). Instead, the knowledge engineer must focus on the problem:
"Which of the known variables are most relevant to the problem?"
- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
\end{enumerate}
\subsection{Structure - Nodes}
The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
\begin{enumerate}
        \item Getting the node values wrong
        \item Node values aren't exhaustive
        \item Node values aren't mutually exclusive
        \item Incorrect modelling of mutually exclusive outcomes
        \item Trying to model fuzzy categories
        \item Confusing state and Probability
        \item Confusion about what the node represents
\end{enumerate}
Two major strategies were employed to overcome these problems. Tying nodes explicitly to a data source that corroberated the definition and state in some manner as the node. For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
\subsection{Structure Arcs}
\subsubsection{Getting the arc directions wrong}
Arc directions are commonly wrong for the following reasons:
\begin{enumerate}
        \item Modelling reasoning rather than causation
        \item Inverting cause and effect
        \item Missing variables
\end{enumerate}
To note: Korb and Nicholson do not actually suggest a method for overcoming these problems. There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation. It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
\subsubsection{Too many parents}
Sometimes it is unavoidable that a node is affected by many factors, or other nodes. There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child. This technique was employed in the creation of the structure of the BN with the expert panel.
\subsection{Parameters}
\subsubsection{Experts estimates of probabilities are biased}
\begin{enumerate}
        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison. "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.

\end{enumerate}
We have attempted to overcome this with two methods. A diverse and varried expert panel. Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale. With some experts being more specialised in specific areas such as agro-chemicals.
\subsubsection{Inconsistent probabilities}
The collection of probabilities for when the CPT is large can result in inconsistent probabilities. The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}. In this study we overcame this through the use of worded response such as high and low. We then assigned probabilities to those broader cases. We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
% \item Inconsistent "filling in" of large CPTs:
-       -       - Being dead certain.
\subsubsection{Incoherent probabilities (not summing to 1)}
We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
\subsubsection{Being dead certain}
It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.
